Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-10-15 paper.tex
Switch to PDF for figures

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.1.png}
\caption{
  Steady solutions for the modulation of short-wave (a) wavenumber, (b)
  gravitational acceleration, (c) amplitude, (d) steepness, (e) intrinsic
  frequency, and (f) intrinsic phase speed as function of long-wave phase for
  $\varepsilon_L = 0.1$, based on
  \citet{longuet1960changes} (L-HS 1960, black) and this paper (blue).
  Long-wave crest and trough are located at $\psi = 0$ and $\psi = \pi$,
  respectively.
}
\label{fig:analytical_solutions_ak0.1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/fig_effective_gravities.png}
\caption{
  (a) Analytical solutions for the effective gravitational acceleration
  modulation by long waves, as function of long-wave phase, for $\varepsilon_L = 0.2$.
  Black is for linear wave evaluated at $z=0$,
  blue and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and without curvature effects,
  and orange and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and with curvature effects.
  (b) As in (a) but normalised by the modulation of the linear wave evaluated at $z=0$, $g_1$.
}
\label{fig:effective_gravities}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_effective_gravities_mean_max_min.png}
\caption{
  As Fig. \ref{fig:effective_gravities} but showing the mean (solid),
  maximum (dashed), and minimum (dotted) short-wave gravity modulation as
  function of long-wave steepness $\varepsilon_L$.
  The minimum and maximum values for the cases with curvature effects
  ($\alpha=\frac{\partial \eta}{\partial x}$) are equivalent to those without
  curvature effects ($\alpha=0$) and obscure them in the plot.
}
\label{fig:effective_gravities_mean_max_min}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_contributors.png}
\caption{
  Contributions of short-wave wavenumber, action, and effective gravity
  modulations to the steepness modulation, as function of the long-wave
  steepness $\varepsilon_L$.
  Panel (a) shows each modulation factor (colour) and their product (black),
  and panel (b) shows their relative contributions in percentage, calculated as
  the ratio of the logarithm of each modulation factor to the logarithm of the
  product of all modulations.
}
\label{fig:modulation_contributors}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions (orange) of wavenumber (top), amplitude
  (middle), and steepness (bottom) modulation with their analytical solutions
  (blue), for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\label{fig:numerical_solutions}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_k.png}
\caption{
  Maximum wavenumber modulation as function of long-wave steepness $\varepsilon_L$.
  Black line and circles are for the analytical and numerical solutions from
  \citet{longuet1960changes} and \citet{longuet1987propagation}, respectively.
  Blue line is based on the analytical solutions from this paper.
  Green and orange lines are for the numerical solutions from this paper
  using linear and third-order Stokes long waves, respectively.
}
\label{fig:numerical_vs_analytical_k}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_a.png}
\caption{
  As Fig. \ref{fig:numerical_vs_analytical_k} but for the amplitude modulation.
}
\label{fig:numerical_vs_analytical_a}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_ak.png}
\caption{
  As Fig. \ref{fig:numerical_vs_analytical_k} but for the steepness modulation.
}
\label{fig:numerical_vs_analytical_ak}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_infinite_wave_train.png}
\caption{
  Change in the short-wave action (left), wavenumber (middle), and steepness (right)
  relative to their initial values as function of initial long-wave phase and time.
  $k_L = 1$, $k = 10$, $\varepsilon_L = 0.1$.
  The black contour follows the value of 1, which corresponds to no change
  from the initial values.
}
\label{fig:modulation_3panel_infinite}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_linear_ramp.png}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but with a linear ramp
  applied to $a_L$ during the initial five long-wave periods.
}
\label{fig:modulation_3panel_ramp}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/fig_modulation_ramp_timeseries.png}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \label{fig:unsteady_growth_timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/inhomogeneity_tendencies.png}
  \caption{
    Propagation ($C_g \frac{\partial N}{\partial x}$) (blue) and inhomogeneity
    ($N \frac{\partial C_g}{\partial x}$) (orange) tendencies and their sum
    (green) for the short-wave action after one long-wave period, in the case of
    (a) infinite long-wave train and (b) linear ramp of long-wave amplitude.
    Dashed line is the long-wave elevation and the dotted line is the short-wave
    action modulation minus 1.
  }
  \label{fig:inhomogeneity_tendencies}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_wave_group.png}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but for a long-wave group,
  causing the long-wave amplitude to gradually increase and peak at $a_L = 0.1$
  after five long-wave periods, and then conversely decay back to a calm sea state.
}
\label{fig:modulation_3panel_groups}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_analytical_solutions_ak0.1.pdf}
\caption{
  Steady solutions for the modulation of short-wave (a) wavenumber, (b)
  gravitational acceleration, (c) amplitude, (d) steepness, (e) intrinsic
  frequency, and (f) intrinsic phase speed as function of long-wave phase for
  $\varepsilon_L = 0.1$, based on
  \citet{longuet1960changes} (L-HS 1960, black) and this paper (blue).
  Long-wave crest and trough are located at $\psi = 0$ and $\psi = \pi$,
  respectively.
}
\label{fig:analytical_solutions_ak0.1}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/fig_effective_gravities.pdf}
\caption{
  (a) Analytical solutions for the effective gravitational acceleration
  modulation by long waves, as function of long-wave phase, for $\varepsilon_L = 0.2$.
  Black is for linear wave evaluated at $z=0$,
  blue and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and without curvature effects,
  and orange and green are for linear and Stokes waves, respectively, evaluated at $z=\eta$ and with curvature effects.
  (b) As in (a) but normalised by the modulation of the linear wave evaluated at $z=0$, $g_1$.
}
\label{fig:effective_gravities}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/fig_effective_gravities_mean_max_min.pdf}
\caption{
  As Fig. \ref{fig:effective_gravities} but showing the mean (solid),
  maximum (dashed), and minimum (dotted) short-wave gravity modulation as
  function of long-wave steepness $\varepsilon_L$.
  The minimum and maximum values for the cases with curvature effects
  ($\alpha=\frac{\partial \eta}{\partial x}$) are equivalent to those without
  curvature effects ($\alpha=0$) and obscure them in the plot.
}
\label{fig:effective_gravities_mean_max_min}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_contributors.pdf}
\caption{
  Contributions of short-wave wavenumber, action, and effective gravity
  modulations to the steepness modulation, as function of the long-wave
  steepness $\varepsilon_L$.
  Panel (a) shows each modulation factor (colour) and their product (black),
  and panel (b) shows their relative contributions in percentage, calculated as
  the ratio of the logarithm of each modulation factor to the logarithm of the
  product of all modulations.
}
\label{fig:modulation_contributors}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.pdf}
\caption{
  Comparison of numerical solutions (orange) of wavenumber (top), amplitude
  (middle), and steepness (bottom) modulation with their analytical solutions
  (blue), for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\label{fig:numerical_solutions}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_k.pdf}
\caption{
  Maximum wavenumber modulation as function of long-wave steepness $\varepsilon_L$.
  Black line and circles are for the analytical and numerical solutions from
  \citet{longuet1960changes} and \citet{longuet1987propagation}, respectively.
  Blue line is based on the analytical solutions from this paper.
  Green and orange lines are for the numerical solutions from this paper
  using linear and third-order Stokes long waves, respectively.
}
\label{fig:numerical_vs_analytical_k}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_a.pdf}
\caption{
  As Fig. \ref{fig:numerical_vs_analytical_k} but for the amplitude modulation.
}
\label{fig:numerical_vs_analytical_a}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/numerical_vs_analytical_solutions_ak.pdf}
\caption{
  As Fig. \ref{fig:numerical_vs_analytical_k} but for the steepness modulation.
}
\label{fig:numerical_vs_analytical_ak}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_infinite_wave_train.pdf}
\caption{
  Change in the short-wave action (left), wavenumber (middle), and steepness (right)
  relative to their initial values as function of initial long-wave phase and time.
  $k_L = 1$, $k = 10$, $\varepsilon_L = 0.1$.
  The black contour follows the value of 1, which corresponds to no change
  from the initial values.
}
\label{fig:modulation_3panel_infinite}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_linear_ramp.pdf}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but with a linear ramp
  applied to $a_L$ during the initial five long-wave periods.
}
\label{fig:modulation_3panel_ramp}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/fig_modulation_ramp_timeseries.pdf}
  \caption{
    Maximum short-wave steepness modulation as function of time in case of
    infinite long-wave train case (blue) and the same case but with a linear
    ramp during the initial five long-wave periods (orange). The dashed black
    line corresponds to the short-wave steepness of 0.4 at which most waves are
    expected to break.
  }
  \label{fig:unsteady_growth_timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/inhomogeneity_tendencies.pdf}
  \caption{
    Propagation ($C_g \frac{\partial N}{\partial x}$) (blue) and inhomogeneity
    ($N \frac{\partial C_g}{\partial x}$) (orange) tendencies and their sum
    (green) for the short-wave action after one long-wave period, in the case of
    (a) infinite long-wave train and (b) linear ramp of long-wave amplitude.
    Dashed line is the long-wave elevation and the dotted line is the short-wave
    action modulation minus 1.
  }
  \label{fig:inhomogeneity_tendencies}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/fig_modulation_3panel_wave_group.pdf}
\caption{
  Same as Fig. \ref{fig:modulation_3panel_infinite} but for a long-wave group,
  causing the long-wave amplitude to gradually increase and peak at $a_L = 0.1$
  after five long-wave periods, and then conversely decay back to a calm sea state.
}
\label{fig:modulation_3panel_groups}
\end{figure}
